Pool Model

### 2025-08-28 pool_model.tex
enhance some figures
add notes for discussion

        A cell right before and after a division event.

@@

    \label{fig:spatial-cell-division-example}

@@

\begin{table}

@@

% ================================================================================================
\section{Discussion}
% ------------------------------------------------------------------------------------------------
\section{Conclusion}
\newpage
\printbibliography

>>>>

        (A) A cell right before and (B) after a division event.

@@

@@

\begin{table}[h]

@@

% ================================================================================================
\section{Discussion}

How well does the pool model do to encapsulate all the different growth models
\begin{itemize}
    \item All 6 models can be represented by pool model
    \item Baranyi-Roberts results can be reproduced, but not identical; requires some work
    \item what are some general limitations within this framework? how can they be circumvented?
\end{itemize}

\noindent
How justified was the construction of the \ac{abm}?
\begin{itemize}
    \item Discuss simplified physical interaction model
    \item Heterogeneity plays a role; as we have shown
    \item why did we not simply use a PDE?; because we have to think in terms of cellular processes
        and this ensures that our model is actually realistic
\end{itemize}

\noindent
How can we cover more effects of bacteria?
\begin{itemize}
    \item More states for metabolic processes
    \item More states for more species
    \item Other cooperiation/inhibition effects
    \item external influences
\end{itemize}

\noindent
What are limitations of our approach?
\begin{itemize}
    \item spatial stuff; heterogeneity (because \ac{ode})
    \item larger models require more parameters, harder to estimate
    \item only simple models have analytical solutions
\end{itemize}

% ------------------------------------------------------------------------------------------------
\section{Conclusion}
\newpage
\printbibliography
